---
title: "report"
author: "yiren"
date: "19/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## import the library

```{r}

```


## Data Cleaning
```{r}

```


## Question 1
A clear statement of the goal of the mini-project (in short sentence(s) and most preferably in the form of (a) question(s) you intend to answer).

```{r}

```

## Question 2
A brief summary of the approach you have followed to achieve your goal. 

```{r}

```

## Question 3
A brief introduction to the problem (what has been done before in this context, why is the problem you are tackling relevant, etc...).

```{r}

```


## Question 4
Comprehensive descriptive analysis of the data (which variables you have available, are they continuous, discrete?, etc...).


```{r}

```

## Question 5

Comprehensive presentation of results (which statistical models/techniques have you used -if any- and why they were adequate to tackle your problem with the data you had).

```{r}


```


## Question 6
Conclusions and discussion.


## Question 7
Possible future work.





