---
title: "10.24 Analysis"
author: "yiren"
date: "24/10/2021"
output: html_document
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, pacman, ggmap, janitor, sf, mapview, leaflet, rgdal, RColorBrewer, ggplot2, data.table, readr, qqplotr, GGally, lubridate, raster, spData, spDataLarge, tmap, osmdata, gifski)

#Register API key to google
register_google(key="AIzaSyBT6yzDKV_DGcFGK9E-cXu0zNUD4WTJOZA")

#Get location of chicago
chicago <- geocode("Chicago, IL")

#Make leaflet map with chicago center
chicago_leaflet <- leaflet() %>% 
  setView(lng=chicago$lon, lat=chicago$lat, zoom=10) %>%
  addProviderTiles(providers$CartoDB.Positron) 


# data("World")
# library(remotes)
# remotes::install_github("ropensci/osmdata")
```

## Load data, clean name and get sample

```{r cars}
mytable <- read_csv("data/taxi_trips_2020.csv") %>%
  clean_names() %>%
  print()

set.seed(123)
my_sample <- mytable %>%
  sample_n(10000)
```

```{r}
glimpse(mytable)
```



## Map for roads and popular areas
We look at the tag of amenities and find plot out the places where people are likely to take taxi.

```{r}
# available_tags("amenity")
load("osm.RData")
# q1 <- getbb("Chicago") %>%
#   opq() %>%
#   add_osm_feature("amenity", "theatre") %>% osmdata_sf()
# 
# q2 <- getbb("Chicago") %>%
#   opq() %>%
#   add_osm_feature("amenity", "restaurant") %>% osmdata_sf()
# 
# q3 <- getbb("Chicago") %>%
#   opq() %>%
#   add_osm_feature("amenity", "hospital") %>% osmdata_sf()
# 
# 
# # str(q4) #query structure
# q_all = c (q1, q2, q3)

```

```{r}
mad_map <- get_map(getbb("Chicago"),  maptype = "roadmap")
ggmap(mad_map) +
  geom_sf(data = q_all$osm_points,inherit.aes = FALSE, colour = "red",size = 0.5, alpha = 0.1) +
  labs(title = "Chicago", subtitle = "41.8781°N / 87.6298°W", x = "", y = "") +xlab("") 
                                                                                       
```



```{r}
mad_map <- get_map(getbb("Chicago"), maptype = "toner-background")

ggmap(mad_map) +
  geom_sf(data = q_all$osm_points,inherit.aes = FALSE, colour = "red",size = 0.5, alpha = 0.1) +
  labs(title = "Chicago", subtitle = "41.8781°N / 87.6298°W", x = "", y = "")  
  # geom_sf(data = airport$osm_points,inherit.aes = FALSE, colour = "black",size = 1, alpha = 0.3)
```


To make the road more visible, we plot the roads out instead.
```{r}
# available_tags("highway")
load("streets.RData")
# big_streets <- getbb("Chicago")%>%
#   opq()%>%
#   add_osm_feature(key = "highway", 
#                   value = c("motorway", "primary", "motorway_link", "primary_link")) %>%
#   osmdata_sf()
# 
# med_streets <- getbb("Chicago")%>%
#   opq()%>%
#   add_osm_feature(key = "highway", 
#                   value = c("secondary", "tertiary", "secondary_link", "tertiary_link")) %>%
#   osmdata_sf()


# small_streets <- getbb("Chicago")%>%
#   opq()%>%
#   add_osm_feature(key = "highway", 
#                   value = c("residential", "living_street",
#                             "unclassified",
#                             "service", "footway"
#                   )) %>%
#   osmdata_sf()

a1 <- st_read("/Users/yirencao/Documents/GitHub/SCV/code/data/chicago_community_areas.shp", as_tibble=T, quiet=T) %>%
  clean_names() %>%
  dplyr::select(area_numbe, community, geometry) %>%
  mutate(geometry = st_geometry(geometry),
         area_numbe = as.factor(area_numbe)) %>% #if this stops working extract it to own variable
  rename(pickup_community_area = area_numbe,
         community_name = community) 

a1_3857 <- sf::st_transform(a1, 3857)
ggplot() +
  geom_sf(data = a1) +
  geom_sf(data = a1_3857, colour = "blue", fill = NA, alpha = .3) +
  geom_sf(data = big_streets$osm_lines,
          inherit.aes = FALSE,
          color = "black",
          size = .3,
          alpha = .3) + 
  geom_sf(data = med_streets$osm_lines,
          inherit.aes = FALSE,
          color = "#666666",
          size = .2,
          alpha = .3) +
  labs(title = "Chicago", subtitle = "41.8781°N / 87.6298°W") +
  theme_void() +
  geom_sf(data = q_all$osm_points,inherit.aes = FALSE, colour = "orange",
          fill = "orange",
          alpha = .1,
          size = 1,
          shape = 21) 
    theme(plot.title = element_text(size = 20, family = "lato", face="bold", hjust=.5), plot.subtitle = element_text(family = "lato", size = 8, hjust=.5, margin=margin(2, 0, 5, 0))) 
```
## Basics

```{r}
summary(sample)
sample_gally <- my_sample %>% dplyr::select(trip_seconds, trip_miles, fare, tips, trip_total)
GGally::ggpairs(sample_gally) + theme_bw(base_size = 22)
```

## Zones vs Revenue
```{r}
zone_rev <- my_sample %>% 
  dplyr::select(pickup_community_area, dropoff_community_area, trip_total) %>%
  mutate(across(c(pickup_community_area, dropoff_community_area),factor))

pickup_zone <- zone_rev %>% 
  dplyr::select(pickup_community_area, trip_total) %>% 
  drop_na() # remove na now

# keep the zones with highest revenue
pick_up_top <- pickup_zone %>%
  group_by(pickup_community_area) %>% 
  summarise(trip_total = sum(trip_total)) %>%
  arrange(desc(trip_total)) %>%
  top_n(10) 

pick_up_top

# pickup_zone %>%
#   filter(pickup_community_area %in% pick_up_top$pickup_community_area) %>% group_by(pickup_community_area) %>% count()

# pickup$pickup_community_area
pickup_zone %>%
  filter(pickup_community_area %in% pick_up_top$pickup_community_area) %>%
  ggplot(aes(x = pickup_community_area, y = trip_total, fill = pickup_community_area)) +
  geom_boxplot() + 
  scale_y_continuous(limits = c(0, 200)) + # we didn't actually remove the outliners, but to better visualise the data, we zoom in the place where we have the boxplots
  scale_fill_brewer(palette="RdBu") +
  theme_classic()
  
```

It is obvious that zone 76 and zone 8 generate the highest total revenue. However, for a single driver, zone 76 and zone 56 might be preferred since they have a higher average (median) revenue per trip.

We prefer using median over mean because the distribution of revenue is skewed.

drop off 
```{r}
dropoff_zone <- zone_rev %>% 
  dplyr::select(dropoff_community_area, trip_total) %>% 
  drop_na() # remove na now

# keep the zones with highest revenue
drop_off_top <- dropoff_zone %>%
  group_by(dropoff_community_area) %>% 
  summarise(trip_total = sum(trip_total)) %>%
  arrange(desc(trip_total)) %>%
  top_n(10) 

dropoff_zone %>%
  filter(dropoff_community_area %in% drop_off_top$dropoff_community_area) %>%
  ggplot(aes(x = dropoff_community_area, y = trip_total, fill = dropoff_community_area)) +
  geom_boxplot() + 
  scale_y_continuous(limits = c(0, 150)) + # we didn't actually remove the outliners, but to better visualise the data, we zoom in the place where we have the boxplots
  theme_classic()
```

### pickup - dropoff pair total revenue
olav's original codes
```{r}
df1 <- my_sample %>%
  group_by(pickup_community_area, dropoff_community_area) %>%
  summarise(total = sum(trip_total)) %>%
  # mutate(total=as.factor(total)) %>%
  drop_na()
df1 %>%  
  ggplot(aes(x=pickup_community_area, y=dropoff_community_area)) +
  geom_point(aes(size = total),alpha = 1/2, colour = "orange") +
  theme_bw()
```
## Average

```{r}
taxi_trips <- mytable
trip_total_in_area <- taxi_trips %>%
  dplyr::select(pickup_community_area, trip_total) %>%
  mutate(pickup_community_area = as.factor(pickup_community_area),
         trip_total = (as.numeric(pickup_community_area))) %>%
  group_by(pickup_community_area) %>%
  summarise(trip_total = sum(trip_total)) 

areas_trip_total <- areas %>%
  inner_join(trip_total_in_area, by="pickup_community_area")

#Trying to color each area by trip_total
revenue_pal <- colorBin("Blues",bins=4, domain =log10(areas_trip_total$trip_total.x), )


#Investigating average time of getting new costumer per area after dropping somebody off (an arbitrary place)

#Preparing relevant dataset 
pickup_dropoff_times <- taxi_trips %>%
  dplyr::select(taxi_id, trip_end_timestamp, trip_start_timestamp, 
         pickup_community_area, dropoff_community_area,
         trip_total, trip_seconds) %>% #for in hourly_rate estimator
  mutate(trip_end_timestamp = as.double(mdy_hms(trip_end_timestamp)),
         pickup_community_area = as.factor(pickup_community_area),
         dropoff_community_area = as.factor(dropoff_community_area),
         trip_start_timestamp = as.double(mdy_hms(trip_start_timestamp)),
         trip_total = as.numeric(trip_total),
         trip_seconds = as.numeric(trip_seconds)) %>%
  drop_na() 

dropoff_times <- pickup_dropoff_times %>% 
  dplyr::select(taxi_id, trip_end_timestamp, dropoff_community_area) %>%
  group_by(taxi_id) %>%
  arrange(trip_end_timestamp, .by_group=TRUE) %>%
  filter(row_number() != n()) 

pickup_times <- pickup_dropoff_times %>%
  dplyr::select(taxi_id, trip_start_timestamp, pickup_community_area,
         trip_total, trip_seconds) %>% 
  group_by(taxi_id) %>%
  arrange(trip_start_timestamp, .by_group=TRUE) %>%
  filter(row_number() != 1) 
```


```{r}
#Dataset used as basis for plotting bost avg time to pickup in each area and
#our expected hourly rate
dropoff_to_pickup <- pickup_times %>%
  add_column(trip_end_timestamp = dropoff_times$trip_end_timestamp, .after=1) %>%
  add_column(dropoff_community_area = dropoff_times$dropoff_community_area, .after=5) 

time_to_pickup <- dropoff_to_pickup %>%
  mutate(time_between = (trip_start_timestamp - trip_end_timestamp)/60) %>%
  filter(pickup_community_area == dropoff_community_area) %>%
  dplyr::select(pickup_community_area, time_between) %>% 
  group_by(pickup_community_area) %>%
  filter(time_between < 300) %>% 
  summarise(avg_pickup_time = mean(time_between, na.rm=TRUE)) 
  
areas_pickup_time <- areas %>%
  inner_join(time_to_pickup, by="pickup_community_area") %>%
  mutate(avg_pickup_time=as.integer(avg_pickup_time)) 

```
```{r}
time_pal <- colorBin("OrRd", domain=areas_pickup_time$avg_pickup_time, bins=c(0, 6, 12, 18, 24, 30), 
                reverse=TRUE, na.color='floralwhite')

#Generate html labels
label_avg_pickup_time <- sprintf(
  "<strong>%s</strong><br/>Average time from dropoff to new pickup:<br/>%g minutes",
  areas_pickup_time$community_name, areas_pickup_time$avg_pickup_time
) %>% lapply(htmltools::HTML)


#Labels for the legend
waiting_time_labels<-c('< 6 minutes', '6 - 12 minutes', '12 - 18 minutes', '18 - 24 minutes', 
         '> 24 minutes')
#Make the map
c1 <- chicago_leaflet %>%
  addPolygons(data=areas_pickup_time,
              fillColor=~time_pal(areas_pickup_time$avg_pickup_time),
              color="lightgrey",
              weight=2,
              fillOpacity=0.8,
              highlightOptions = highlightOptions(
                weight=3,
                opacity=2,
                color="azure1",
                bringToFront=TRUE),
              label=label_avg_pickup_time,
              labelOptions=labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>%
  
  addLegend("bottomright",
            pal = time_pal,
            labFormat = function(type, cuts, p) {  # To get custom labels
              paste0(waiting_time_labels)
            },
            values = areas_pickup_time$avg_pickup_time,
            title = "Average time between pickup and dropoff",
            opacity = 0.8) %>%
  addResetMapButton()
```
```{r}
c1
```


```{r}
time_pal <- colorBin("OrRd", domain=areas_pickup_time$avg_pickup_time, bins=c(0, 6, 12, 18, 24, 30), 
                reverse=TRUE, na.color='floralwhite')

#Generate html labels
label_avg_pickup_time <- sprintf(
  "<strong>%s</strong><br/>Average time from dropoff to new pickup:<br/>%g minutes",
  areas_pickup_time$community_name, areas_pickup_time$avg_pickup_time
) %>% lapply(htmltools::HTML)


#Labels for the legend
waiting_time_labels<-c('< 6 minutes', '6 - 12 minutes', '12 - 18 minutes', '18 - 24 minutes', 
         '> 24 minutes')
#Make the map
chicago_leaflet %>%
  addPolygons(data=areas_pickup_time,
              fillColor=~time_pal(areas_pickup_time$avg_pickup_time),
              color="lightgrey",
              weight=2,
              fillOpacity=0.8,
              highlightOptions = highlightOptions(
                weight=3,
                opacity=2,
                color="azure1",
                bringToFront=TRUE),
              label=label_avg_pickup_time,
              labelOptions=labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>%
  
  addLegend("bottomright",
            pal = time_pal,
            labFormat = function(type, cuts, p) {  # To get custom labels
              paste0(waiting_time_labels)
            },
            values = areas_pickup_time$avg_pickup_time,
            title = "Average time between pickup and dropoff",
            opacity = 0.8)
```


```{r}
# average trip total per trip per area / (average waiting time + average trip time for each area) 

avg_hourly_rate <- dropoff_to_pickup %>%
  mutate(waiting_time = (trip_start_timestamp - trip_end_timestamp)/60) %>%
  filter(pickup_community_area == dropoff_community_area) %>%
  filter(waiting_time < 300) %>%##remove outliers which indicate end of workday
  group_by(pickup_community_area) %>%
  print()
```


## Population vs Zones

```{r}
comm_area = read_csv("data/mywiki.csv")
comm_area_1 = comm_area %>% 
  dplyr::select(No., Population) %>% 
  rename(pickup_community_area = No.) %>%
  mutate(pickup_community_area = as.numeric(pickup_community_area)) %>%
  mutate(pickup_community_area = as.factor(pickup_community_area)) 


## modified olav's codes
areas <- st_read("/Users/yirencao/Documents/GitHub/SCV/code/data/chicago_community_areas.shp", as_tibble=T, quiet=T) %>%
  clean_names() %>%
  dplyr::select(area_numbe, community, geometry) %>%
  mutate(geometry = st_geometry(geometry),
         area_numbe = as.factor(area_numbe)) %>% #if this stops working extract it to own variable
  rename(pickup_community_area = area_numbe,
         community_name = community) %>%
  inner_join(comm_area_1, by="pickup_community_area") %>%
  print()

print(areas)
#Trying to color each area by Population
pal <- colorBin("Oranges",bins=4, domain =log2(areas$Population))

#Generate html labels
labels <- sprintf(
  " <strong>%s</strong><br/>Population: %g",
  areas$community_name, areas$Population
) %>% lapply(htmltools::HTML)


# pal <- colorNumeric("viridis", NULL)


#Make the map
chicago_leaflet %>%
  addPolygons(data=areas,
              fillColor=~pal(log2(areas$Population)),
              color="lightgrey",
              weight=2,
              fillOpacity=0.8,
              highlightOptions = highlightOptions(
                weight=3,
                opacity=2,
                color="azure1",
                bringToFront=TRUE),
              label=labels,
              labelOptions=labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>%
  
  addLegend("bottomright",
            pal = pal,
            values = log2(areas$Population),
            title = "Population",
            opacity = 0.8,
            labFormat = leaflet::labelFormat(
              transform = function(x) round(2^(x))))
```
## Taxi Company
```{r}
pal <- colorBin("Oranges",bins=4, domain =log2(areas$Population))

#Generate html labels
labels <- sprintf(
  " <strong>%s</strong><br/>Population: %g",
  areas$community_name, areas$Population
) %>% lapply(htmltools::HTML)
chicago_leaflet %>%
  addPolygons(data=areas,
              fillColor=~pal(log2(areas$Population)),
              color="lightgrey",
              weight=2,
              fillOpacity=0.8,
              highlightOptions = highlightOptions(
                weight=3,
                opacity=2,
                color="azure1",
                bringToFront=TRUE),
              label=labels,
              labelOptions=labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>%
  
  addLegend("bottomright",
            pal = pal,
            values = log2(areas$Population),
            title = "Population",
            opacity = 0.8,
            labFormat = leaflet::labelFormat(
              transform = function(x) round(2^(x))))

```


## Time vs Zones
```{r}
# sample %>% group_by(pickup_community_area, company) %>% count()
```

```{r}
world
tm_shape(areas) + tm_polygons()  + tm_dots(size = "Population") 

new_mytable <- mytable %>% 
  mutate(pickup_community_area = as.factor(pickup_community_area))
# area_time <- areas %>%
#   inner_join(new_mytable, by="pickup_community_area") %>%
#   print() # run too long
```

```{r}

my_sample$trip_start=(paste(substr(my_sample$trip_start_timestamp,12,13),substr(my_sample$trip_start_timestamp,21,22)))



my_sample$trip_start[my_sample$trip_start == "12 AM"] <- 1
my_sample$trip_start[my_sample$trip_start == "01 AM"] <- 2
my_sample$trip_start[my_sample$trip_start == "02 AM"] <- 3
my_sample$trip_start[my_sample$trip_start == "03 AM"] <- 4
my_sample$trip_start[my_sample$trip_start == "04 AM"] <- 5
my_sample$trip_start[my_sample$trip_start == "05 AM"] <- 6
my_sample$trip_start[my_sample$trip_start == "06 AM"] <- 7
my_sample$trip_start[my_sample$trip_start == "07 AM"] <- 8
my_sample$trip_start[my_sample$trip_start == "08 AM"] <- 9
my_sample$trip_start[my_sample$trip_start == "09 AM"] <- 10
my_sample$trip_start[my_sample$trip_start == "10 AM"] <- 11
my_sample$trip_start[my_sample$trip_start == "11 AM"] <- 12
my_sample$trip_start[my_sample$trip_start == "12 PM"] <- 13
my_sample$trip_start[my_sample$trip_start == "01 PM"] <- 14
my_sample$trip_start[my_sample$trip_start == "02 PM"] <- 15
my_sample$trip_start[my_sample$trip_start == "03 PM"] <- 16
my_sample$trip_start[my_sample$trip_start == "04 PM"] <- 17
my_sample$trip_start[my_sample$trip_start == "05 PM"] <- 18
my_sample$trip_start[my_sample$trip_start == "06 PM"] <- 19
my_sample$trip_start[my_sample$trip_start == "07 PM"] <- 20
my_sample$trip_start[my_sample$trip_start == "08 PM"] <- 21
my_sample$trip_start[my_sample$trip_start == "09 PM"] <- 22
my_sample$trip_start[my_sample$trip_start == "10 PM"] <- 23
my_sample$trip_start[my_sample$trip_start == "11 PM"] <- 24

```

```{r}

# For each zone, for each hour, count the number total avenue

zone_time <- my_sample %>% 
  group_by(pickup_community_area, trip_start) %>% 
  summarise(trip_total = sum(trip_total)) %>% 
  mutate(pickup_community_area = as.factor(pickup_community_area), trip_start = as.numeric(trip_start))


```


```{r}
# urb_anim = tm_shape(world) + tm_polygons() + 
#   tm_shape(urban_agglomerations) + tm_dots(size = "population_millions") +
#   tm_facets(along = "year", free.coords = FALSE)
# tmap_animation(urb_anim, filename = "urb_anim.gif", delay = 25)


areas <- st_read("/Users/yirencao/Documents/GitHub/SCV/code/data/chicago_community_areas.shp", as_tibble=T, quiet=T) %>%
  clean_names() %>%
  dplyr::select(area_numbe, community, geometry) %>%
  mutate(geometry = st_geometry(geometry),
         area_numbe = as.factor(area_numbe)) %>% #if this stops working extract it to own variable
  rename(pickup_community_area = area_numbe,
         community_name = community) %>%
  # full_join(zone_time, by="pickup_community_area") %>%
  print()

zone_time_poly <- areas %>%
  full_join(zone_time, by="pickup_community_area") %>%
  drop_na() %>% st_as_sf()

# adding two layers
my_anim = tm_shape(areas) + tm_polygons() + tm_shape(zone_time_poly) + tm_polygons("trip_total", palette = "Blues") + tm_dots(size = "trip_total", col = "red") + tm_facets(along = "trip_start", free.coords = FALSE) 

# But only a sample is used
tmap_animation(my_anim, filename = "my_anim3.gif", delay = 35)

```


Now we map to the whole dataset
```{r}

my_sample <- mytable
my_sample$trip_start=(paste(substr(my_sample$trip_start_timestamp,12,13),substr(my_sample$trip_start_timestamp,21,22)))

my_sample$trip_start[my_sample$trip_start == "12 AM"] <- 1
my_sample$trip_start[my_sample$trip_start == "01 AM"] <- 2
my_sample$trip_start[my_sample$trip_start == "02 AM"] <- 3
my_sample$trip_start[my_sample$trip_start == "03 AM"] <- 4
my_sample$trip_start[my_sample$trip_start == "04 AM"] <- 5
my_sample$trip_start[my_sample$trip_start == "05 AM"] <- 6
my_sample$trip_start[my_sample$trip_start == "06 AM"] <- 7
my_sample$trip_start[my_sample$trip_start == "07 AM"] <- 8
my_sample$trip_start[my_sample$trip_start == "08 AM"] <- 9
my_sample$trip_start[my_sample$trip_start == "09 AM"] <- 10
my_sample$trip_start[my_sample$trip_start == "10 AM"] <- 11
my_sample$trip_start[my_sample$trip_start == "11 AM"] <- 12
my_sample$trip_start[my_sample$trip_start == "12 PM"] <- 13
my_sample$trip_start[my_sample$trip_start == "01 PM"] <- 14
my_sample$trip_start[my_sample$trip_start == "02 PM"] <- 15
my_sample$trip_start[my_sample$trip_start == "03 PM"] <- 16
my_sample$trip_start[my_sample$trip_start == "04 PM"] <- 17
my_sample$trip_start[my_sample$trip_start == "05 PM"] <- 18
my_sample$trip_start[my_sample$trip_start == "06 PM"] <- 19
my_sample$trip_start[my_sample$trip_start == "07 PM"] <- 20
my_sample$trip_start[my_sample$trip_start == "08 PM"] <- 21
my_sample$trip_start[my_sample$trip_start == "09 PM"] <- 22
my_sample$trip_start[my_sample$trip_start == "10 PM"] <- 23
my_sample$trip_start[my_sample$trip_start == "11 PM"] <- 24
```


```{r}
zone_time <- my_sample %>% 
  group_by(pickup_community_area, trip_start) %>% 
  summarise(trip_total = sum(trip_total)) %>% 
  mutate(pickup_community_area = as.factor(pickup_community_area), trip_start = as.numeric(trip_start))

# areas <- st_read("/Users/yirencao/Documents/GitHub/SCV/code/data/chicago_community_areas.shp", as_tibble=T, quiet=T) %>%
#   clean_names() %>%
#   dplyr::select(area_numbe, community, geometry) %>%
#   mutate(geometry = st_geometry(geometry),
#          area_numbe = as.factor(area_numbe)) %>% #if this stops working extract it to own variable
#   rename(pickup_community_area = area_numbe,
#          community_name = community) %>%
#   # full_join(zone_time, by="pickup_community_area") %>%
#   print()

zone_time_poly <- areas %>%
  full_join(zone_time, by="pickup_community_area") %>%
  drop_na() %>% st_as_sf()

# adding two layers
my_anim = tm_shape(areas) + tm_polygons() + tm_shape(zone_time_poly)  + tm_bubbles(size = "trip_total", col = "orange") + tm_facets(along = "trip_start", free.coords = FALSE) 

# But only a sample is used
tmap_animation(my_anim, filename = "my_anim_whole.gif", delay = 25)


```


```{r}
temp <- areas %>%
  full_join(zone_time, by="pickup_community_area")
temp
```

