---
title: "SCV Analysis"
author: "yiren"
date: "19/10/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(data.table)
library(dplyr)
library(readr)
library(qqplotr)
library(GGally) 
library(leaflet)
library(lubridate) # dealing with time
library(nycflights13)

library(sf)
library(raster)
library(dplyr)
library(spData)
library(spDataLarge)
library(tmap)    # for static and interactive maps
library(osmdata)
library(ggmap)

```


## Previous
```{r}
mytable <- read_csv("data/taxi_trips_2020.csv")
```

```{r}
pacman::p_load(pacman, party, psych, rio, tidyverse, plotly, rjson, corrr) 
p_load(janitor)
taxi_trips = mytable %>% clean_names() %>%
  print()

```

```{r}
set.seed(5)
sample <- taxi_trips %>%
  sample_n(10000)
```

```{r}

```

## explore the relationship among continuous variables

frequency data, age - man/woman, woman - distribution, - stratify

interactive,


```{r}
summary(sample)
sample_gally <- taxi_trips %>%
  sample_n(10000)

sample_gally <- sample_gally %>% dplyr::select(trip_seconds, trip_miles, fare, tips, trip_total)
GGally::ggpairs(sample_gally) + theme_bw(base_size = 22)
```

As expected, trip miles and trip total have strong positive correlation.
While looking at the histogram of the continous variables, we can spot the pattern that most of the distribution have heavy tails, hence we do the logrithmic transformation.


```{r}
ggplot(sample_gally, aes(x = trip_total)) +
  geom_histogram(binwidth = 3) + xlim(0, 150)

```

```{r}
ggplot(sample_gally, aes(x = trip_total)) +
  geom_histogram() +  scale_y_continuous(trans='log2') + scale_x_continuous(trans='log2') 
```


```{r}
ggplot(sample_gally, aes(x = trip_total)) +
  geom_histogram(binwidth = 5) +  scale_y_continuous(trans='log2') + xlim(0, 200)
```

From the plot, it seems like that trip_total.. to be continue

## Analysis
```{r}
par(cex = 0.3) 
sample %>% 
  ggplot(mapping = aes(sample = trip_total)) +
    stat_qq_band() +
    stat_qq_line() +
    stat_qq_point() +
    labs(x = "Theoretical Quantiles", y = "Sample Quantiles") + 
    theme_classic() + theme(aspect.ratio=1) +
    theme(text = element_text(size=6)) + 
  scale_y_continuous(limits = c(0, 400)) # use scale y to ignore the extreme outliners.
```


```{r}
# library(ggfortify) 
# lm1 = lm(lozone ~ temperature, data = environmental)
# autoplot(lm1, which = 1:2)
```



## explore other maps

```{r}
q1 <- getbb("Chicago") %>%
  opq() %>%
  add_osm_feature("amenity", "cinema") 

q2 <- getbb("Chicago") %>%
  opq() %>%
  add_osm_feature("amenity", "restaurant")
  # add_osm_feature(key = 'route', value = 'train')
str(q1) #query structure
q_all = c (osmdata_sf (q1), osmdata_sf (q2))
# spots <- osmdata_sf(q_all)
# bus
```



```{r}
# plots all spots
mad_map <- get_map(getbb("Chicago"), maptype = "toner-background")
  ggmap(mad_map)+
  geom_sf(data = q_all$osm_points,inherit.aes = FALSE)+ 
  labs(x = "", y = "") 
```

```{r}
get_map(getbb("Chicago"), maptype = "toner-background")
  ggmap(mad_map)+
  geom_sf(data = q_all$osm_points,inherit.aes = FALSE, colour = "red",size = 0.5, alpha = .3)+
  labs(x = "", y = "") 
```



```{r cars}
# #loading useful packages
# pacman::p_load(pacman, party, psych, rio, tidyverse) 
# p_load(janitor)
# 
# taxi_trips <- import("data/taxi_trips.csv") %>%
#   as_tibble() %>%
#   clean_names() %>% #from janitor package to remove space from names
#   print()
# 
# 


# 
# df1 <- sample %>%
#   mutate(pickup_community_area = as.numeric(pickup_community_area)) %>%
#   select(pickup_community_area, trip_total) %>%
#   mutate(trip_total, scale) %>% #standardize c("y", "z"), ~(scale(.) %>% as.vector)
#   group_by(pickup_community_area) %>%
#   arrange(pickup_community_area) %>%
#   summarise(total = sum(trip_total, na.rm=T)) %>%
#   #hist(df1$pickup_community_area, df1$total) 
#   print()
# 
# ?mutate_at  

# min(df1[1], na.rm = T) # 1
# 
# max(df1[1], na.rm = T) # 77 
```

# Variables we use are pickup_community_area, dropoff_community_area, trip_total


## Loading from main
```{r}
#I want to start with exploring the relationships between pickup and dropoff locations in terms of revenue
df1 <- taxi_trips %>%
  select(pickup_community_area, dropoff_community_area, trip_total) %>%
  mutate(pickup_community_area = as.numeric(pickup_community_area),
         dropoff_community_area = as.numeric(dropoff_community_area),
         trip_total=as.numeric(trip_total))

#Extracting a random sample so plotting is done more quickly
sample <- df1 %>%
  sample_n(10000)

#initial distribution of amount of taxitips -> almost all trips start from the same areas
sample %>%
  ggplot() +
  geom_bar(mapping=aes(x=pickup_community_area)) #set fill to company to see bigest acteurs
  
#Question: which areas?
trips_region <- sample %>%
  group_by(pickup_community_area) %>%
  summarize(count=n()) %>%
  drop_na() 

trips_region %>%
  top_n(n=20, count) %>%
  ggplot(mapping=aes(x=reorder(pickup_community_area, -count), y=count)) +
  geom_bar(stat="identity")

#How does this translate into revenue? (per trip)

mean_trip_region <- sample %>%
  group_by(pickup_community_area) %>%
  drop_na() %>%
  summarize(mean=mean(trip_total)) 

mean_trip_region %>%
  top_n(n=20, mean) %>%
  ggplot(mapping=aes(x=reorder(pickup_community_area, -mean), y=mean)) +
  geom_col() 
  
#Not very informative -> How is the correlation between activity in an area and revenue per trip?

mean_count <- inner_join(trips_region, mean_trip_region)
mean_count %>%
  select(count, mean) %>%
  corrr::correlate(method="pearson")

corrr::corxrelate(mean_count, method = "pearson")

#No correlation detected
```

## Loading from taxi.R
```{r}
#How are the trips distributed over the day?
# sample <- df1 %>%
#   sample_n(10000)
# 
# sample %>%
#   group_by(pickup_community_area, dropoff_community_area) %>%
#   summarise(total = sum(trip_total)) %>%
#   mutate(total=as.factor(total)) %>%
#     ggplot() +
#     geom_point(mapping=aes(x=pickup_community_area, y=dropoff_community_area, size=total))

df1 %>%
  ggplot() +
  geom_histogram(mapping=aes(x=pickup_community_area), binwidth=1)

monthly_trips <- taxi_trips %>%
  select(trip_start_timestamp) %>%
  mutate(trip_start_timestamp = lubridate::mdy_hms(trip_start_timestamp)) %>%
  group_by(month = lubridate::month(trip_start_timestamp), hour = lubridate::hour(trip_start_timestamp)) %>%
  mutate(count = n()) %>%
  print()
```

## Copied from haakonmd (not running yet)
```{r}
library(tidyverse)
library(ggmap)
# taxi_trips<-read_csv("./data/Taxi_Trips_2020.csv")

taxi_trips <- mytable
# Insert of private API key below
register_google(key="###############################")

# Geocode of Chicago
chicago <- geocode("Chicago, IL")

#Displaying pick up Location
pick_up <- tibble(lat=sample$`Pickup Centroid Latitude`, lon=sample$`Pickup Centroid Longitude`)

ggmap(get_map(chicago, zoom=11, maptype="toner-lite"))+
  ggtitle("Pick up locations for a sample of 10 000 taxi trips")+
  geom_point(mapping=aes(x=lon, y=lat), color="black", data=pick_up, alpha=0.05)+
  theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.title=element_blank()) +
  theme(panel.background=element_blank())


#Displaying drop off Location
drop_off <- tibble(lat=sample$`Dropoff Centroid Latitude`, lon=sample$`Dropoff Centroid Longitude`)

ggmap(get_map(chicago, zoom=11, maptype="toner-lite"))+
  ggtitle("Drop off locations for a sample of 10 000 taxi trips")+
  geom_point(mapping=aes(x=lon, y=lat), color="black", data=drop_off, alpha=0.05)+
  theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.title=element_blank()) +
  theme(panel.background=element_blank())
```




## Dataset

```{r}
head(sample)
```


You can also embed plots, for example:
### 1. Direct Calc w/o Standardization

```{r pressure, echo=FALSE}
sample %>%
  mutate(pickup_community_area = as.numeric(pickup_community_area)) %>%
  select(pickup_community_area, trip_total) 


mytrip = taxi_trips %>%
  mutate(pickup_community_area = as.numeric(pickup_community_area)) %>%
  select(pickup_community_area, trip_total) %>% 
  group_by(pickup_community_area) %>%
  summarise(total = sum(trip_total, na.rm=T)) %>%
  # arrange(desc(total)) %>%
  rename(comm = pickup_community_area) %>% drop_na()


```
It shows community 76 is the one getting most revenue, however, when we look at the area data, community 76 O'Hare is obviously the largest community in Chicago.

### 2. Considering Area
Area data
https://en.wikipedia.org/wiki/Community_areas_in_Chicago#cite_note-CMAP_Area-10

Geospatial Data
https://data.cityofchicago.org/Facilities-Geographic-Boundaries/Boundaries-Community-Areas-current-/cauq-8yn6

Data Cleaning 
```{r}
comm_area = read_csv("data/mywiki.csv")
comm_area_1 = comm_area %>% 
  select(No., `Area(km2)`) %>% 
  rename(comm = No.) %>%
  mutate(comm = as.numeric(comm))
  
```

Join the two dataframes by the community code
```{r}
revenue_area = merge(mytrip, comm_area_1)
revenue_area %>% mutate(standard_rev = total/`Area(km2)`) %>% arrange(desc(standard_rev))
```
just look at data
```{r}
comm_area %>% arrange(desc(`Density(km2)`))
comm_area %>% arrange(desc(Population))
```





